Bathtub Qualitative Reasoning

### 2016-10-21 paper.tex
paper

\begin{itemize}
\item I+(Inflow, Volume): the amount of inflow increases the volume
\item I-(Outflow, Volume): the amount of outflow decreases the volume
\item P+(Volume, Outflow): outflow changes are proportional to volume changes
\item V(Volume(Max), Outflow(Max)): the outflow is at its highest value (Max), when the volume is at it highest value
\item V(Volume(0), Outflow(0)): there is no outflow, when there is no volume
\end{itemize}
\end{itemize}

@@

\subsection{Modelling choices and possible extensions}
The implemented algorithm is very general and it allows to model an arbitrarily complex model. Despite that we decided not to include certain features in our program.

@@

\section{Trace}

@@

\item \textbf{Dependencies:}
\begin{itemize}
\item I+(Inflow, Volume): the amount of inflow increases the volume
\item I-(Outflow, Volume): the amount of outflow decreases the volume
\item P+(Volume, Height): height changes are proportional to volume changes
\item P+(Height, Pressure): pressure changes are proportional to height changes
\item P+(Pressure, Outflow): outflow changes are proportional to pressure changes
\item V(Volume(Max), Height(Max)): the height is at its highest value (Max), when the volume is at it highest value
\item V(Volume(0), Height(0)): there is no height, when there is no volume
\item V(Height(Max), Pressure(Max)): the pressure is at its highest value (Max), when the height is at it highest value
\item V(Height(0), Pressure(0)): there is no pressure, when there is no height
\item V(Pressure(Max), Outflow(Max)): the outflow is at its highest value (Max), when the pressure is at it highest value
\item V(Pressure(0), Outflow(0)): there is no outflow, when there is no pressure
\end{itemize}
\end{itemize}

\begin{figure}[H]
\centering
\includegraphics[scale=0.4]{problem_extra.eps}
\caption{Drawings of the causal model active for the extra problem}
\end{figure}

>>>>

\begin{itemize}
\item I+(Inflow, Volume): the amount of inflow increases the volume
\item I-(Outflow, Volume): the amount of outflow decreases the volume
\item P+(Volume, Outflow): outflow changes are proportional to volume changes
\item VC(Volume(Max), Outflow(Max)): the outflow is at its highest value (Max), when the volume is at it highest value
\item VC(Volume(0), Outflow(0)): there is no outflow, when there is no volume
\end{itemize}
\end{itemize}

@@

\subsection{Modeling choices and possible extensions}
The implemented algorithm is very general and it allows to model an arbitrarily complex model. Despite that we decided not to include certain features in our program.

@@

\section{Trace}
In order to debug the code and let users to better understand what the algorithm do we print a trace. The trace of the base problem is in \texttt{base\_trace} file and the trace of the extra problem is in \texttt{extra\_trace} file.

@@

\item \textbf{Dependencies:}
\begin{itemize}
\item I+(Inflow, Volume): the amount of inflow increases the volume
\item I-(Outflow, Volume): the amount of outflow decreases the volume
\item P+(Volume, Height): height changes are proportional to volume changes
\item P+(Height, Pressure): pressure changes are proportional to height changes
\item P+(Pressure, Outflow): outflow changes are proportional to pressure changes
\item VC(Volume(Max), Height(Max)): the height is at its highest value (Max), when the volume is at it highest value
\item VC(Volume(0), Height(0)): there is no height, when there is no volume
\item VC(Height(Max), Pressure(Max)): the pressure is at its highest value (Max), when the height is at it highest value
\item VC(Height(0), Pressure(0)): there is no pressure, when there is no height
\item VC(Pressure(Max), Outflow(Max)): the outflow is at its highest value (Max), when the pressure is at it highest value
\item VC(Pressure(0), Outflow(0)): there is no outflow, when there is no pressure
\end{itemize}
\end{itemize}

\begin{figure}[H]
\centering
\includegraphics[scale=0.5]{problem_extra.eps}
\caption{Drawings of the causal model active for the extra problem}
\end{figure}
